\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
Changes in the Introduction

MapReduce belongs among the most popular frameworks for data parallel
computation. A MapReduce program~\cite{dean04} consists of several pairs
of \emph{mappers} and \emph{reducers} running on a machine cluster for handling
big data in parallel. Usually, mappers and reducers are the only components in a
MapReduce program that involve concurrency. Mappers read data from a distributed
database and output a sequence of \emph{key-value} pairs. The elements of the
sequence (i.e., key-value pairs) with the same key are sent to the same reducer
for further processing. Due to scheduling policies and network latency, the same
inputs may arrive at a reducer in different orders in different executions.
Therefore, reducers are typically required to be \emph{commutative}, that is,
the output of a reducer is required to be independent of the order of its
inputs. The problem of checking whether this is indeed the case is known as the
\emph{commutativity problem} of
reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}. If all reducers
are commutative, they will have the same external behaviour under all possible
schedules. 
One then suffices with considering any chosen interleaving
of input values instead of all of them.
In such a case, by fixing a schedule, the verification problem of a
MapReduce program can be reduced to the verification problem of a sequential
program, which is known to be much easier than the verification problem of
concurrent~programs.

@@

In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
Verifier). A link to J-ReCoVer can be found in the supplementary materials. The
tool implements a heuristic approach for checking the commutativity problem
that---despite its simplicity---works very efficiently on a large set of
practical integer reducer programs as shown by our experiments. The main
ingredient of the approach is a reduction from the commutativity problem to an
SMT problem. The reduction is incomplete but sound. It is accompanied with
several heuristics which enable the approach to scale to real-world examples.
For the case when the reducer is not proven commutative, we complement the
approach by using testing to find concrete counterexamples.

>>>>

MapReduce belongs among the most popular frameworks for data parallel
computation. A MapReduce program~\cite{dean04} consists of several pairs of
\emph{mappers} and \emph{reducers} running on a machine cluster for handling big
data in parallel. Usually, mappers and reducers are the only components in a
MapReduce program that involve concurrency. Mappers read data from a distributed
database and output a sequence of \emph{key-value} pairs. The elements of the
sequence (i.e., key-value pairs) with the same key are sent to the same reducer
for further processing. Due to scheduling policies and network latency, the same
inputs may arrive at a reducer in different orders in different executions.
Therefore, reducers are typically required to be \emph{commutative}, that is,
the output of a reducer is required to be independent of the order of its
inputs. The problem of checking whether this is indeed the case is known as the
\emph{commutativity problem} of
reducers~\cite{csallner13testing,xiao14mr,ChenHSW15,ChenSW16}.

If a reducer is commutative, it will have the same external behaviour under all
possible schedules, and one then suffices with considering any chosen
interleaving of input values when examining its behaviour instead of having to
consider all of them. By fixing a schedule, the verification problem of a
MapReduce program reduces to the verification problem of a sequential program,
which is known to be much easier than the verification problem of
concurrent~programs.

@@

In this paper, we present the J-ReCoVer tool (Java Reducer Commutativity
Verifier), which is available at~\verb|http://www.jrecover.tk/|.
%
% A link to J-ReCoVer can be found in the supplementary materials.
%
The tool implements a heuristic approach for checking the commutativity problem
that---despite its simplicity---works very efficiently on a large set of
practical integer reducer programs as shown by our experiments. The main
ingredient of the approach is a reduction from the commutativity problem to an
SMT problem. The reduction is incomplete but sound. It is accompanied with
several heuristics which enable the approach to scale to real-world examples.
For the case when the reducer is not proven commutative, we complement the
approach by using testing to find concrete counterexamples.
